\pdftitle

### 2017-05-15 maxNt.tex
start discussion
add luca's ackn

%% Author: PGL  Porta Mana
%% Created: 2015-11-04T09:20:08+0100
%% Last-Updated: 2017-05-15T11:42:02+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Report-no: ***
\documentclass{article}

@@

\definecolor{notecolour}{RGB}{68,170,153}
\newcommand*{\puzzle}{{\fontencoding{U}\fontfamily{fontawesometwo}\selectfont\symbol{225}}}
\newcommand*{\mynote}[1]{ {\color{notecolour}\puzzle\ #1}}
\newcommand*{\widebar}[1]{{\mkern1.5mu\skew{2}\overline{\mkern-1.5mu#1\mkern-1.5mu}\mkern 1.5mu}}

@@

\mynote{We don't give an answer. Different purposes. Bright side: no real
  contradiction because we are expressing two states of knowledge, not
  physical situations. Also, in some case numerically very similar results.
  Same phenomenon in statistical mechanics \cite{maesetal1999}. Somehow
  similar quandary for equilibrium state at the end of non-equilibrium
  process: Gibbs state vs initial Gibbs state + Liouville
  evolution \cite[\sect~4]{jaynes1985d_r1993}; but in this case both
  distributions are immensely sharp, and this doesn't affect predictions}

@@

Use unnumbered third level headings for the acknowledgments. All
acknowledgments go at the end of the paper. Do not include
acknowledgments in the anonymized submission, only in the final paper.

>>>>

%% Author: PGL  Porta Mana
%% Created: 2015-11-04T09:20:08+0100
%% Last-Updated: 2017-05-15T11:55:06+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Report-no: ***
\documentclass{article}

@@

\definecolor{notecolour}{RGB}{68,170,153}
\newcommand*{\puzzle}{{\fontencoding{U}\fontfamily{fontawesometwo}\selectfont\symbol{225}}}
\newcommand{\mynote}[1]{ {\color{notecolour}\puzzle\ #1}}
\newcommand*{\widebar}[1]{{\mkern1.5mu\skew{2}\overline{\mkern-1.5mu#1\mkern-1.5mu}\mkern 1.5mu}}

@@

\mynote{We don't give an answer. Different purposes. Bright side: no real
  contradiction because we are expressing two states of knowledge, not
  physical situations. Also, in some case numerically very similar results.

  The distribution obtained from the population-level application has lower
  entropy; this usually means that in includes additional assumptions than
  the other. Intuitively, this additional assumption is that the $n$
  neurons are part of a larger population, of which they are
  representative.

  Same phenomenon in statistical mechanics \cite{maesetal1999}. Somehow
  similar quandary for equilibrium state at the end of non-equilibrium
  process: Gibbs state vs initial Gibbs state + Liouville
  evolution \cite[\sect~4]{jaynes1985d_r1993}; but in this case both
  distributions are immensely sharp, and this doesn't affect predictions}

@@

PGLPM thanks Mari \amp\ Miri for continuous encouragement and affection,
Buster Keaton for filling life with awe and inspiration, and the developers
and maintainers of \LaTeX, Emacs, AUC\TeX, MiK\TeX, arXiv, biorXiv,
PhilSci, Hal archives, Python, Inkscape, Sci-Hub for making a free and
unfiltered scientific exchange possible.

% Use unnumbered third level headings for the acknowledgments. All
% acknowledgments go at the end of the paper. Do not include
% acknowledgments in the anonymized submission, only in the final paper.
